Social Computing Article\thanks{This title is temporary}

### 2013-01-06 Article.tex
Corrigi algumas coisas no meu texto, adicionei a referência pro mason e fiz o merge

\section{Methodology}

We developed a system in which the environment of the sudoku problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments. The optimization technique of {\em Memetic Networks}~\cite{lamb:memenet} was employed on the modelling, giving a basis for the dynamics of the agent network. A {\em Memetic Network Algorithm} is composed of an ordered set of $N$ agents, each encoding a complete solution to the optimization problem, and a binary $N \times N$ matrix encoding possible connections between agents. Additionally, a {\em Memetic Network Algorithm} is composed of a set of rules specifying how connections between agents are formed and erased and how interactions between these agents take place. These rules are grouped under the categories of {\em Connection Rules}, specifying how agents will connect and disconnect from each other; {\em Aggregation Rules}, specifying the dynamics of the information flow through connections; and {\em Appropriation Rules}, specifying how agents are supposed to add local changes to the information received through their connections.

@@

The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings. For instance, the authors analysis has shown that users tend to copy not the most complete solutions, but instead the first solutions on the graphic interface. Additionally, we know from that same paper that users rarely copy solutions from more than 6 neighbours. In order to analyse and compare this behaviours, we developed a collection of aggregation rules, each modelling a copying strategy.

@@

We inserted this behaviour into our model by firstly generating a random ordering of neighbours for each agent to compose a simulated graphic interface in which each agent visualizes some neighbours before or after others. Secondly, we translated the above mathematical model into an aggregation rule in which the solution copied by an agent is the $k_{th}$ solution with probability $X(k)$.

@@

In sudoku strategy literature, as in chess, we find multiple techniques with iconic names. Some popular examples are {\em naked singles}, {\em naked twins}, {\em swordfish}. These strategies intend to, given a sudoku puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as "{\em mark cell 1 of column 3 with value 5}". We reproduced a variety of these strategies, modelling each one of them as a function mapping a sudoku partial solution to a set of movements.

@@

This technique proceeds to mark a sudoku cell with a value only if this cell is the last blank cell on its row, column or $3 \times 3$ block. For instance, the {\em only choice} rule would mark cell $(1,2)$ with value $4$ in the below sudoku puzzle:

@@

This rule marks a sudoku cell with value $v$ only if $v$ is the single possible value to mark that cell. The other values must have been eliminated through a process of verifying that they are all present in the span encompassing the cell's row, column and $3 \times 3$ block. For instance, the {\em single possibility} rule would mark cell $(4,1)$ with value $7$ in the below sudoku puzzle, since the values $1$,$2$,$3$,$4$,$5$ and $8$ were already present in the cell's column (leaving the possibilities $6$,$7$ and $9$) and the values $6$ and $9$ were already present in the cells' row (leaving the single possibility $7$).

@@

This rule works on a group of three contiguous $3 \times 3$ blocks. It aims to find a value $v$ such that $v$ is present in two of the three $3 \times 3$ blocks encompassed by the group, but missing on the third. It then proceeds by enumerating all the candidate cells (namely the empty cells) on this block, and then eliminating from this set all the cells that are encompassed by the rows or columns in which $v$ is placed on the other two blocks. If the resulting set has cardinality $1$, the rule has successfully found one cell to mark. For instance, the {\em two out of three} rule would mark cell $(2,9)$ with value $1$.

>>>>

\section{System Overview}

We developed a system in which the environment of the sudoku problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments. The optimization technique of {\em Memetic Networks}~\cite{lamb:memenet} was employed on the modelling, providing a basis for the dynamics of the agent network.

\section{Sudoku Solving Memetic Network}

A {\em Memetic Network Algorithm} is composed of an ordered set of $N$ agents, each encoding a complete solution to the optimization problem, and a binary $N \times N$ matrix representing possible connections between agents. Additionally, a {\em Memetic Network Algorithm} is composed of a set of rules specifying how connections between agents are formed and erased and how interactions between these agents take place. These rules are grouped under the categories of {\em Connection Rules}, specifying how agents will connect and disconnect from each other; {\em Aggregation Rules}, specifying the dynamics of the information flow through connections; and {\em Appropriation Rules}, specifying how agents are supposed to add local changes to the information received through their connections~\cite{lamb:memenet}.

@@

The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings. For instance, the authors analysis has shown that users tend to copy not the most complete solutions, but, instead, the first solutions on the graphic interface. Additionally, we know from this same paper that users rarely copy solutions from more than 6 neighbours. In order to analyse and compare this behaviours, we developed a collection of aggregation rules, each modelling a copying strategy.

@@

We inserted this behaviour into our model by firstly generating a random ordering of neighbours for each agent in order to compose a simulated graphic interface. As a result, each agent visualizes some neighbours before or after others. Secondly, we translated the above mathematical model into an aggregation rule in which the solution copied by an agent is the $k_{th}$ with probability $X(k)$.

@@

In sudoku strategy literature, as in chess, we find multiple techniques with iconic names. Some popular examples are {\em naked singles}, {\em naked twins}, {\em swordfish}. These strategies intend to, given a sudoku puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as "{\em mark cell 1 of column 3 with value 5}". We reproduced a variety of these strategies, modelling each one of them as a function that maps a sudoku partial solution to a set of movements.

@@

This technique marks a sudoku cell with a value only if this cell is the last blank cell on its row, column or $3 \times 3$ block. For instance, the {\em only choice} rule would mark cell $(1,2)$ with value $4$ in the below sudoku puzzle:

@@

This rule marks a sudoku cell with value $v$ only if $v$ is the single possible value to mark that cell. The other values must have been eliminated through a process of verifying that they are all present in the span encompassing the cell's row, column and $3 \times 3$ block. For instance, the {\em single possibility} rule would mark cell $(4,1)$ with value $7$ in the below sudoku puzzle, since the values $1$, $2$, $3$, $4$, $5$ and $8$ were already present in the cell's column (leaving the possibilities $6$, $7$ and $9$). Additionally, the values $6$ and $9$ were already present in the cells' row, thus leaving the single possibility $7$.

@@

This rule applies to groups of three contiguous $3 \times 3$ blocks. It aims to find a value $v$ such that $v$ is present in two of the three $3 \times 3$ blocks encompassed by the group, but missing on the third. It proceeds by enumerating all the candidate cells - namely the empty cells - on this block, and then, by eliminating from this set all the cells that are encompassed by the rows or columns in which $v$ is placed on the other two blocks. If the resulting set has cardinality $1$, the rule has successfully found one cell to mark. For instance, the {\em two out of three} rule would mark cell $(2,9)$ with value $1$ on the below sudoku.
